Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-08-11 manuscript/manuscript.tex
Changes in manuscript

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/Dexp-power-differences.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thin spherical shell of 1km of thickness and the exponential density defined on equation \ref{eq:density-exp} for different values of $b$. Each computation was performed on the big grid described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 10$^{-1}\%$, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-exp-power}
\end{figure}

@@

As a final case, we propose to perform the same test with a discontinuous density function:

@@

\noindent where $\rho_1$ and $\rho_2$ are constant densities, $R_1$ and $R_2$ are the inner and outer radii of the shell, respectively, and $R_c$ is the the radii on which the 
density changes.

\todo{poner solucion analitica}

First we assume a symmetric density function, i.e. $R_c=(R_1 + R_2)/2$ is the centre radius of the shell, and perform the test for a thin shell of 1km of thickness.
The results can be seen in Figure \ref{fig:D-discont-sym}.
Again, we obtain good accuracy for values of $D=$1,2 and 8 for the computation of the potential, the gradient components and the Marussi tensor components, respectively.

@@

Secondly, lets assume the same density function from equation \ref{eq:density-discontinuous}, but now with an asymmetrical distribution such as $R_c = (R_1 + R_2)/3$, and perform the same test.
We can see its results in Figure \ref{fig:D-discont-asym}: up to $D=10$ the difference between the numerical model and the analytical solution is greater than 10\%, what
lead us to conclude that the code does not reassembles the gravity fields for this case with good accuracy.

>>>>

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/Dexp-power-differences.pdf}
\caption{
    Differences between the Marussi tensor component $g_{zz}$ generated by the numerical model and the analytical solution for (a) a thin spherical shell of 1km of thickness and (b) a thick sphericall shell of 35km of thickness, both with the exponential density defined on equation \ref{eq:density-exp}. Each computation was performed on the big grid described in Table \ref{tab:grids}, for different values of the distance-size ratio $D$ and $b$. If the difference is less than 10$^{-1}\%$, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-exp-power}
\end{figure}

@@

As a final case, we performed the same test with a discontinuous density function:

@@

\noindent where $\rho_1$ and $\rho_2$ are constant densities, $R_1$ and $R_2$ are the inner and outer radii of the shell, respectively, and $R_c$ is the the radius on which the 
density changes.

The analytical solution for this kind of density is the linear combination of two homogeneous shells with densities $\rho_1$ and $\rho_2$:

\begin{equation}
    V(r) = \frac{4}{3} \frac{\pi G}{r}
    \left[ \rho_1 (R_c^3 - R_1^3) +
    \rho_2 (R_2^3 - R_c^3) \right]
\end{equation}

Firstly, lets assume a symmetric density function, i.e. $R_c=(R_1 + R_2)/2$ is the centre radius of the shell, and perform the test for a thin shell of 1km of thickness.
The results can be seen in Figure \ref{fig:D-discont-sym}.
Again, we obtain good accuracy for values of $D=$1,2 and 8 for the computation of the potential, the gradient components and the Marussi tensor components, respectively.

@@

Secondly, lets assume the same density function from equation \ref{eq:density-discontinuous}, but now with an asymmetrical distribution: $R_c = (R_1 + R_2)/3$, and perform the same test.
We can see its results in Figure \ref{fig:D-discont-asym}: up to $D=10$ the difference between the numerical model and the analytical solution is greater than 10\%, what
lead us to conclude that the code does not reassembles the gravity fields for this case with good accuracy.
